---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggois

<!-- badges: start -->
<!-- badges: end -->

The goal of `ggois` is to make plots for in O&S style. 

## Installation

You can install the released version of ggois from [github](https://github.com/brilstl/ggois) with:

```{r}
# install.packages("devtools")
devtools::install_github("brilstl/ggois")
```

## Example

This is a basic example of a plot with the `theme_ois()` function:

```{r example}

library(ggois)
library(tidyverse)

diamonds %>% 
  ggplot(
  aes(
    x = price,
    y = cut
  )
) +
  geom_boxplot(colour = os_colours$red) +
  theme_ois()

```

`ggois` also has some convenient to make tables and plots. The packags works with a basic idea of algebra formulation such as `y ~ x`. With a possible moderator, namely: `y ~ x*z`. 

# bar plot

```{r cars}
example_bar <- diamonds %>% 
  ggois_bar_chart(cut, price)


example_bar
```

## plot

```{r}
example_bar %>% 
  autoplot()
```

## table

```{r}
example_bar %>% 
  autotable()
```

# likert plot

```{r}
example_likert <- diamonds %>% 
  ggois_likert_chart(cut, clarity)


example_likert
```

## plot

```{r}
example_likert %>% 
  autoplot()
```

## table

```{r}
example_likert %>% 
  autotable()
```


